\sysfull

### 2018-04-17 paper/hwswsetup.tex
methodology: minor edits

\textbf{Comparison with Alpaca using the GCC compiler.} We compare
\sys against Alpaca~\cite{alpaca}, a state-of-the-art task-based system for
intermittent computing. For a fair comparison the task decomposition is the
same in both \sys and Alpaca implementations of the benchmarks. We compare
both systems using GCC, the compiler with the best performance for the
MSP430 architecture.

Since Alpaca's compiler pass is implemented only for LLVM, we could not use it
to instrument the benchmarks and compile them with GCC. Instead, we
\emph{manually} performed the instrumentation done by the compiler pass.
We performed the instrumentation at the source level, adding C
statements to the program, instead of at the level of binary
intermediate-representation (LLVM IR) as the compiler pass would. The result is
equivalent from the perspective of overheads. The
instrumentation consists of identifying write-after-read dependencies and
adding code and memory allocations to make a private copy of the
affected variables. For array variables, instrumentation also includes adding
code and memory allocations to track the first write to the array.

>>>>

\textbf{Comparison with Alpaca using the GCC compiler.} We compare
\sys against Alpaca~\cite{alpaca}, a state-of-the-art task-based system for
intermittent computing. For a fair comparison the task decomposition is the
same in \sys and Alpaca implementations of the benchmarks. We compare
both systems using GCC, the compiler with the best performance for the
MSP430 architecture.

Since Alpaca's compiler pass is implemented only for LLVM, we could not use
that implementation to instrument the benchmarks and compile them with GCC.
Instead, we \emph{manually} performed the instrumentation done by the compiler
pass.  We performed the instrumentation at the source level, adding C
statements to the program, instead of at the level of binary
intermediate-representation (LLVM IR) as the compiler pass would. The result is
equivalent from the perspective of overheads. The instrumentation consists of
identifying write-after-read dependencies and adding code and memory
allocations to make a private copy of the affected variables. For array
variables, instrumentation also includes adding code and memory allocations to
track the first write to the array.
